### 2020-11-21 pldi21/intro.tex
merge

    \begin{subfigure}[t]{\linewidth}
     \begin{snugshade}
      \vspace*{-2mm}
      \caption{\textbf{This Paper:} Livelits are live and compositional}
      \vspace*{1mm}
     \end{snugshade}
      \vspace*{1.5mm}
      \includegraphics[width=\linewidth]{slider-color-livelits.png}
    \end{subfigure}
  \end{minipage}
  \hspace{3mm}
  \begin{subfigure}[t]{0.585\textwidth}
  \begin{snugshade}
   \vspace*{-2mm}
    \caption{\textbf{Case Study}: Grading with Livelits}
    \vspace*{1mm}
     \end{snugshade}
    \vspace*{1.5mm}
    \includegraphics[width=\linewidth]{grade-cutoff-livelit.png}
  \end{subfigure}
   \caption{
   (a) This figure, adapted from the prior work of \citet{Graphite},
   shows a Graphite palette associated with the \texttt{Color} class.
   The client can specify the RGBA components only using literal numbers.
   (b) A similar Hazel livelit for colors uses live splices for the RGBA components,
   so the client can enter any Hazel expression.
   In this case, the client has entered a variable, itself defined using a slider livelit, into the RGB
   splices. The A splice is filled directly with a slider livelit.
   The color livelit evaluates splices under its closure to display the
   computed color.
   The value of \li{default\_color} is determined by the livelit via a macro expansion step.}
   \label{fig:color}
\end{figure*}

>>>>

    \begin{subfigure}[t]{\linewidth}
     \begin{snugshade}
      \vspace*{-2mm}
      \caption{\textbf{This Paper:} Livelits are live and compositional}
      \vspace*{1mm}
     \end{snugshade}
      \vspace*{1.5mm}
      \includegraphics[width=\linewidth]{slider-color-livelits.png}
    \end{subfigure}
  \end{minipage}
  \hspace{3mm}
  \begin{subfigure}[t]{0.585\textwidth}
  \begin{snugshade}
   \vspace*{-2mm}
    \caption{\textbf{Case Study}: Grading with Livelits}
    \vspace*{1mm}
     \end{snugshade}
    \vspace*{1.5mm}
    \includegraphics[width=\linewidth]{grade-cutoff-livelit.png}
  \end{subfigure}
   \caption{}
   \label{fig:color}
\end{figure*}
